Inferring Invariants of Distributed Programs

### 2015-03-04 Doc/approach.tex
dataflow details

>>>>

So we are planning to do a dynamic dataflow analysis which consists of follwing steps:
\begin{itemize}
\item Instrumenting variable declarations and assignments at the run time
\item Collecting execution traces of each of these statements by runnning test suites
\item Doing a forward flow analysis using the collected traces
\end{itemize}

This dynamic analysis approach was chosen because it gives information about the actual execution and therefore is more accurate. And also compared to using a static analysis-based approach, this approach makes it easier to handle Go language-specific constructs like channels which are used share data between goroutines. Only drawback in this approach is, it only examines the paths invoked during execution, unlike static analysis which can be used to reason about all possible execution paths and variable values. To compensate for that we are planning to use a comprehnsive test suite with good test coverage.
